Political Support in the United States

### 2024-03-16 paper/paper.qmd
Update paper.qmd

Throughout the paper, the data utilized for analysis, including both survey and census data, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. I will also talk about the predicted results derived from the model in Section 4. Lastly, Section 5 contains the results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt 2024).

@@

Define the population: The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022. Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.

Gather Data: Acquire information regarding the total number of confirmed survey cases. This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.

Determine the Time Period: Specify the time frame to calculate when the survey object was collected. The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election. The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.

Calculate the Case: Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.

>>>>

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).

@@

**Define the Population:** The survey involves 60,000 cases, based on the survey of adult participants in the fall of 2022. Individual respondents participate in the survey, which is designed to record various information related to electoral behavior, political perspectives, and demographic characteristics.

**Gather Data:** Acquire information regarding the total number of confirmed survey cases. This dataset should include various factors such as,  election experiences, contextual data, demographic details, political affiliations, and viewpoints on diverse policy matters.

**Determine the Time Period:** Specify the time frame to calculate when the survey object was collected. The timeframe is relevant to survey participants about their opinions, voting intentions in the 2022 election. The first period is the pre-election data collection that occurred from September 29 to November 8, 2022, and the second period is post- election data gathered from November 10 to December 15, 2022.

**Calculate the Case:** Calculate each individual's distribution to the survey object. And consider the outcome that will be given with the distributions.
